---
title: "The Yoga Collaborative Instructor Payroll"
format: 
  pdf: 
    pdf-engine: xelatex
params:
  iname: "Elaine Cody"
  pdata: |-
          [{"hourly_pay_rate":"Year 7","pp7":8,"cap":130,"base0":15,"base1":45}]
  cdata: |-
          [{"instructor":"Elaine Cody","date":"Dec 5, 2023","time":"8:00am","short_service":"Slow Vinyasa Flow","stype":"Classes","at.s":9,"lc.s":0,"at.v":4,"total":13,"hourly_pay_rate":"Year 7","final_pay":101},{"instructor":"Elaine Cody","date":"Dec 5, 2023","time":"9:30am","short_service":"Gentle Yoga for EVERY Body","stype":"Classes","at.s":20,"lc.s":0,"at.v":8,"total":28,"hourly_pay_rate":"Year 7","final_pay":221},{"instructor":"Elaine Cody","date":"Dec 7, 2023","time":"9:30am","short_service":"Gentle Yoga for EVERY Body","stype":"Classes","at.s":18,"lc.s":0,"at.v":5,"total":23,"hourly_pay_rate":"Year 7","final_pay":181},{"instructor":"Elaine Cody","date":"Dec 7, 2023","time":"11:00am","short_service":"Gentle Therapeutic Yoga for Building Better Balance","stype":"Events","at.s":13,"lc.s":0,"at.v":1,"total":14,"hourly_pay_rate":"Event Rate 70%","final_pay":171.5},{"instructor":"Elaine Cody","date":"Dec 12, 2023","time":"8:00am","short_service":"Slow Vinyasa Flow","stype":"Classes","at.s":10,"lc.s":0,"at.v":5,"total":15,"hourly_pay_rate":"Year 7","final_pay":117},{"instructor":"Elaine Cody","date":"Dec 12, 2023","time":"9:30am","short_service":"Gentle Yoga for EVERY Body","stype":"Classes","at.s":21,"lc.s":1,"at.v":4,"total":26,"hourly_pay_rate":"Year 7","final_pay":205},{"instructor":"Elaine Cody","date":"Dec 14, 2023","time":"9:30am","short_service":"Gentle Yoga for EVERY Body","stype":"Classes","at.s":20,"lc.s":0,"at.v":6,"total":26,"hourly_pay_rate":"Year 7","final_pay":205},{"instructor":"Elaine Cody","date":"Dec 17, 2023","time":"3:00pm","short_service":"Honoring the Winter Solstice Candlelight Flow & Restorative Rest","stype":"Events","at.s":13,"lc.s":1,"at.v":2,"total":16,"hourly_pay_rate":"Event Rate 70%","final_pay":327.6},{"instructor":"Elaine Cody","date":"Dec 19, 2023","time":"8:00am","short_service":"Slow Vinyasa Flow","stype":"Classes","at.s":14,"lc.s":0,"at.v":3,"total":17,"hourly_pay_rate":"Year 7","final_pay":133},{"instructor":"Elaine Cody","date":"Dec 19, 2023","time":"9:30am","short_service":"Gentle Yoga for EVERY Body","stype":"Classes","at.s":19,"lc.s":0,"at.v":5,"total":24,"hourly_pay_rate":"Year 7","final_pay":189},{"instructor":"Elaine Cody","date":"Dec 21, 2023","time":"9:30am","short_service":"Gentle Yoga for EVERY Body","stype":"Classes","at.s":13,"lc.s":0,"at.v":3,"total":16,"hourly_pay_rate":"Year 7","final_pay":125},{"instructor":"Elaine Cody","date":"Dec 28, 2023","time":"9:30am","short_service":"Gentle Yoga for EVERY Body","stype":"Classes","at.s":19,"lc.s":0,"at.v":10,"total":29,"hourly_pay_rate":"Year 7","final_pay":229},{"instructor":"Elaine Cody","date":"Dec 17, 2023","time":"3:00pm","stype":"Events","at.s":0,"lc.s":0,"at.v":2,"total":2}] 
---

```{r setup}
#| echo: false
#| results: hide
#| message: false
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
library(tidyverse)
library(knitr)
library(dplyr)
library(gt)
library(scales)
```

```{r class-instructor-variables}
pdata <- jsonlite::fromJSON(params$pdata)
ctable <- jsonlite::fromJSON(params$cdata)
ipay <- sum(ctable$final_pay, na.rm = TRUE)
```

Dear `r params$iname`,

Please find the details below based on the classes you taught at TYC this month.
The calculation of your payout is based on the following parameters:

| Base 0 Clients          | Base 1+ Clients         | PP7 (\*)              | Cap                   |
|-------------------------|-------------------------|-----------------------|-----------------------|
| `r dollar(pdata$base0)` | `r dollar(pdata$base1)` | `r dollar(pdata$pp7)` | `r dollar(pdata$cap)` |

(\*) PP7 = Per person starting with 7th Student

The classes you taught are shown below: (if you taught a virtual class as well, the total represents the combined number of clients)

```{=tex}
\begingroup\setlength{\LTleft}{0pt minus 500pt}\setlength{\LTright}{0pt minus 500pt}\fontsize{5pt}{7pt}\selectfont\addtolength{\tabcolsep}{-3pt}
```
```{r tbl, results='asis'}
#| include: true
#| echo: false

gt(ctable[2:12], rowname_col = "instructor") |>
   fmt_currency(columns = final_pay) |>
   fmt_integer(columns = c(at.s, lc.s, at.v, total)) |>
   cols_label(date = "Date", time = "Time", short_service = "Service",
              stype = "Stype", at.s = "Studio", lc.s = "LateC", at.v = "Virtual",
              ex = "Ex",
              total = "Total", hourly_pay_rate = "Hourly Pay Rate",
              final_pay = "Pay") |>
  as_latex()
```

```{=tex}
\endgroup
```
Total Pay = `r dollar(ipay)`

Created on `r format(Sys.Date(), "%B %d, %Y")`
