---
title: "Monthly Payroll"
format: html
editor: visual
params:
  month: "03"
  year: "2024"
  payroll_folder_url: "https://drive.google.com/drive/folders/1si6xal0w6JPyy-m7RVm3zJ9q7n0tf2tm"
  google_user_email: "andymaffei@gmail.com"
  payrate_file_name: "tyc-payrates"
  payroll_csv_prefix: "tyc_wlpayroll"
  instructor_file_name: "tyc-instructors"
  payroll_csvs_folder_name: "payroll_csvs"
  instructor_pdfs_folder_name: "instructor_pdfs"
---

## TYC Monthly Payroll

This is a log of the monthly payroll run for The Yoga Collaborative.

## Initialize the payroll run

```{r initialize-run}
#| echo: false
#| include: false
#| results: hide

# Clear workspace

# Load required libraries
library(tidyverse)
library(shiny)
library(quarto)
library(googledrive)
library(googlesheets4)
library(gt)

# Authorize google sheets access 
gs4_auth(email=params$google_user_email)

# Authenticate with Google Drive
drive_auth(email=params$google_user_email)

# Extract the ID from the URL
payroll_folder_id <- gsub(".*/folders/(.*)$", "\\1", 
                  params$payroll_folder_url)

# Get directory listing for the top level payroll folder
payroll_folder_dirlist <- drive_ls(path = 
                                     as_id(payroll_folder_id))

# Get payrate spreadsheet reference from dirlist
payrate_file <-  payroll_folder_dirlist |>
  filter(name == params$payrate_file_name)

# Get instructor spreadsheet reference from dirlist
instructor_file <- payroll_folder_dirlist |>
  filter(name == params$instructor_file_name)

# Get payroll folder reference from dirlist
payrollcsvs_folder <- payroll_folder_dirlist |>
  filter(name == params$payroll_csvs_folder_name)

# Get instructor pdf folder ref from dirlist
instructorpdf_folder <- payroll_folder_dirlist |>
  filter(name == params$instructor_pdfs_folder_name)

instructorpdf_dirlist <- drive_ls(path = 
                                     as_id(instructorpdf_folder$id))

# Delete all files in PDF folder
drive_trash(file = instructorpdf_dirlist)

# Create local csv and pdf subdirectories
dir.create("csvs",showWarnings = FALSE)
dir.create("instructor_pdfs",showWarnings = FALSE)

```

## Get Payrate Table for this month

```{r get-payrate-table}
#| echo: false
#| include: true

# Generate payrate table
payrate_tbl <- read_sheet(payrate_file$id) |>
  rename(
    hourly_pay_rate = `WL Hourly Payrate`,
    pp7 = PP7,
    cap = Cap,
    base0 = `Base 0`,
    base1 = `Base 1 Plus`)

# Display the table in the report
gt(payrate_tbl, rowname_col = "hourly_pay_rate") |>
   fmt_currency(columns = c(cap, base1, pp7, base0)) |>
   cols_label(hourly_pay_rate = "Hourly Pay Rate", 
              cap = "Cap", 
              base1 = "Base 1",
              pp7 = "PP7",
              base0 = "Base 0")
```

## Get Instructor Table for this Month

```{r get-instructor-table}
#| echo: false
#| include: true

# Generate Instructor Table

instructor_tbl <- read_sheet(instructor_file$id) |>
  rename(
    name = Name,
    instructor_pay_rate = 'Hourly Pay Rate',
    anniversary_date = 'Anniversary Date'
  )

# Display the table in the report
gt(instructor_tbl) |>
   cols_label(name = "Name", 
              instructor_pay_rate = "Hourly Pay Rate",
              anniversary_date = "Anniversary Date")
```

## Read this months WL Payroll CSV file

```{r read-this-months-payroll-csv}
#| echo: false
#| include: true

# Get directory listing for the top level payroll folder
payrollcsvs_folder_dirlist <- drive_ls(path = 
                                     as_id(payrollcsvs_folder$id))

# Construct the folder and file names
payroll_file_name <- paste("tyc_wlpayroll-",
                           params$year,
                           params$month,".csv",
                           sep = "")

# Find the csv file
payrollcsv_file <-  payrollcsvs_folder_dirlist |>
  filter(name == payroll_file_name)

# Download the file
drive_download(payrollcsv_file$id, 
               overwrite = TRUE)

# Read the file into a tibble
services_held <- read_csv(
  payroll_file_name,
  col_types = cols(
    s_staff.text_fullname = col_character(),
    Client = col_skip(),
    Email = col_skip(),
    Phone = col_skip(),
    `Member ID` = col_skip(),
    Day = col_character(),
    Time = col_character(),
    # Day = col_date(format = "%b %d, %Y"),
    # Time = col_time(format = "%I:%M%p"),
    `Service Name.` = col_character(),
    `Service Type` = col_character(),
    `Commission Sales` = col_skip(),
    Booked = col_integer(),
    Attended = col_integer(),
    `No shows` = col_skip(),
    `Late Cancels` = col_integer(),
    `Base Rate` = col_skip(),
    Bonus = col_skip(),
    Total = col_character(),
    `Tip Amount` = col_skip(),
    `Hourly Pay Rate` = col_character(),
  )
)

# Cleanup - rename columns and adjust

services_held <- services_held |>
    mutate(wl_calc_pay = parse_number(Total)) |>
    mutate(short_service = ifelse(
      grepl("^ *[Ii][Nn] [Ss][Tt][Uu][Dd][Ii][Oo] *", `Service Name.`),
      gsub("^ *[Ii][Nn] [Ss][Tt][Uu][Dd][Ii][Oo] *", "",`Service Name.`),
      gsub("^ *Virtual via Zoom *", "", `Service Name.`))) |>
    rename(instructor = s_staff.text_fullname,
           date = Day,
           time = Time,
           service_name = `Service Name.`,
           service_type = `Service Type`,
           bk  = Booked,
           at = Attended,
           lc = `Late Cancels`,
           total = Total,
           hourly_pay_rate = `Hourly Pay Rate`
           )

gt(services_held)
```

## Convert the WL Payroll file to our own liking

##### Merge studio and virtual into single classes

```{r merge-studio-and-virtual}
#| echo: false
#| include: true

# Split the table based on Service Names starting with "IN STUDIO"
s_services <- services_held |>
  filter(grepl("[Ii][Nn] [Ss][Tt][Uu][Dd][Ii][Oo]", service_name))

# Split the table based on Service Names starting with "Virtual via Zoom"
v_services <- services_held |>
  filter(grepl("Virtual via Zoom", service_name))

# Join columns from v_services to s_services and calculate attendees
# changing NAs to 0
combined_sv <- s_services |>
  left_join(v_services, by = c(
    "instructor", "date", "time", "service_type" ),
    relationship = "one-to-one",
    suffix = c(".s",".v"))

# Generate a table of rows in v_services that did not match rows in s_services
v_services_not_in_s_services <- v_services |>
  anti_join(s_services, by = c(
    "instructor", "date", "time", "service_type", "short_service")) |>
  rename(
    service_name.v = service_name,
    bk.v = bk,
    at.v = at,
    lc.v = lc,
    total.v = total,
    hourly_pay_rate.v = hourly_pay_rate,
    wl_calc_pay.v = wl_calc_pay,
    short_service.v = short_service
  )
  
# Append these rows to combined_sv
combined_sv <- bind_rows(combined_sv, v_services_not_in_s_services)

# Change NAs to 0 for people counts
combined_sv <- combined_sv |>
  mutate(bk.s = ifelse(is.na(bk.s), 0, bk.s)) |>
  mutate(at.s = ifelse(is.na(at.s), 0, at.s)) |>
  mutate(lc.s = ifelse(is.na(lc.s), 0, lc.s)) |>
  mutate(bk.v = ifelse(is.na(bk.v), 0, bk.v)) |>
  mutate(at.v = ifelse(is.na(at.v), 0, at.v)) |>
  mutate(lc.v = ifelse(is.na(lc.v), 0, lc.v)) |>
  mutate(wl_calc_pay.s = ifelse(is.na(wl_calc_pay.s), 0, wl_calc_pay.s)) |>
  mutate(wl_calc_pay.v = ifelse(is.na(wl_calc_pay.v), 0, wl_calc_pay.v)) |>
  mutate(total_attendees = at.s + lc.s + at.v)
```

##### Add base, pp7, and cap based on hourly payrate WL attaches to service offered

```{r add-payrate-columns-by-hourly-payrate-name-for-class}
#| echo: false
#| include: true

# Add base0, base1, pp7, and cap rates as columns by referencing payrate table

combined_sv_w_pay <- combined_sv |>
  left_join(payrate_tbl, by = c("hourly_pay_rate.s" = "hourly_pay_rate")) |>
  rename(
    pp7 = pp7,
    cap = cap,
    base0 = base0,
    base1 = base1
  )

```

##### Calculate base_pay, bonus_pay, and total_pay for each service/class

```{r calculate-pay-per-class}
#| echo: false
#| include: true

# Add the base_pay column for classes
combined_sv_w_pay <- combined_sv_w_pay |>
  mutate(
    base_pay = ifelse(service_type == "Classes" & total_attendees == 0,
                           base0,
                           base1),
    bonus_pay = ifelse(service_type == "Classes" & total_attendees - 6 > 0,
                            (total_attendees - 6) * pp7,
                            0),
    final_pay = ifelse(service_type == "Classes",
                            base_pay + bonus_pay,
                            0))

# Cap the final_pay column for classes
combined_sv_w_pay <- combined_sv_w_pay |>
  mutate(final_pay = ifelse(service_type == "Classes" & final_pay > cap,
                            cap,
                            final_pay))

```

##### Calculate pay for events by adding in-studio and virtual and applying given event rate

```{r}
#| echo: false
#| include: true

# Add the final_pay column for events
# Note that WL has already calculated the pay for events using 70%
combined_sv_w_pay <- combined_sv_w_pay |>
  mutate(final_pay = ifelse(service_type == "Events",
                            (wl_calc_pay.s + wl_calc_pay.v) * 1.0,
                            final_pay))
```

##### Create smaller table with fewer columns with nicer names

```{r}
#| echo: false
#| include: true

services_data_all <- combined_sv_w_pay |>
  select(instructor, date, time, short_service.s, service_type, 
         at.s, lc.s, at.v, total_attendees, hourly_pay_rate.s, final_pay) |>
  rename(
    short_service = short_service.s,
    hourly_pay_rate = hourly_pay_rate.s,
    total = total_attendees,
    stype = service_type)

# Print out table
gt(services_data_all)
```

## Create a summary of pay issued to all instructors

```{r}
#| echo: false
#| include: true

# Create a summary table of services_data_all by instructor
services_data_summary <- services_data_all |>
  group_by(instructor) |>
  summarize(
    classes = sum(stype == "Classes"),
    participants = sum(total),
    pay = sum(final_pay),
  )

# Print out summary
gt(services_data_summary)
```

## Generate Instructor PDF files

```{r generate-instructor-pdfs}
#| echo: false
#| include: false

unique_instructors <- unique(combined_sv_w_pay$instructor)

for (i in 1:NROW(unique_instructors)) {
  # grab instructor name
    instructor_name <- unique_instructors[i] # Each row is a unique instructor
    
  # get instructor payinfo by looking in instructor_tbl by instructor_name
   instructor_payrate <- instructor_tbl |>
      filter(name == instructor_name) |>
      select(instructor_pay_rate)
    
  # get payrate data by looking in payrate_tbl by instructor
    payrate_data <- payrate_tbl |>
      filter(hourly_pay_rate == instructor_payrate$instructor_pay_rate) |>
      select(hourly_pay_rate, pp7, cap, base0, base1)
    
  # get service data by looking in combined_sv_w_pay by instructor
    service_data <- services_data_all |>
      filter(instructor == instructor_name)
    
  # render the template
    quarto::quarto_render(
        input = "template2.qmd",
        output_file = paste0("payroll-", instructor_name, ".pdf"),
        execute_params = list(
            iname = instructor_name,
            pdata = jsonlite::toJSON(payrate_data),
            cdata = jsonlite::toJSON(service_data) # Serialize the data frame
        )
    )
    
  # upload the pdf to the pdf folder
    drive_upload(paste0("payroll-", instructor_name, ".pdf"),
                 path = instructorpdf_folder$id,
                 overwrite = TRUE)
    # Move the pdf to the instructor_pdfs folder
    file.rename(paste0("payroll-", instructor_name, ".pdf"),
                paste0("instructor_pdfs/payroll-", instructor_name, ".pdf"))
    
}
```

## All Done!!!!

```{r cleanup}
# Delete csv files

```
