---
title: "The Yoga Collaborative Instructor Payroll"
format: 
  pdf: 
    pdf-engine: xelatex
params:
  iname: "Elaine Cody"
  pdata: |-
          [{"hourly_pay_rate":"Sub Rate","pp7":4,"cap":120,"base0":15,"base1":40}]
  cdata: |-
          [{"instructor":"Chelsea Winters","date":"Aug 1, 2025","time":"8:00am","short_service":"Slow Flow","stype":"Class","at.s":5,"lc.s":0,"at.v":0,"total":5,"hourly_pay_rate":"Year 3","final_pay":40},{"instructor":"Chelsea Winters","date":"Aug 8, 2025","time":"8:00am","short_service":"Slow Flow","stype":"Class","at.s":8,"lc.s":1,"at.v":0,"total":9,"hourly_pay_rate":"Year 3","final_pay":61},{"instructor":"Chelsea Winters","date":"Aug 15, 2025","time":"8:00am","short_service":"Slow Flow","stype":"Class","at.s":5,"lc.s":0,"at.v":0,"total":5,"hourly_pay_rate":"Year 3","final_pay":40},{"instructor":"Chelsea Winters","date":"Aug 22, 2025","time":"8:00am","short_service":"Slow Flow","stype":"Class","at.s":11,"lc.s":0,"at.v":0,"total":11,"hourly_pay_rate":"Year 3","final_pay":75},{"instructor":"Chelsea Winters","date":"Aug 29, 2025","time":"8:00am","short_service":"Slow Flow","stype":"Class","at.s":9,"lc.s":1,"at.v":0,"total":10,"hourly_pay_rate":"Year 3","final_pay":68}]  
---

```{r setup}
#| echo: false
#| results: hide
#| message: false
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
library(tidyverse)
library(knitr)
library(dplyr)
library(gt)
library(scales)
library(lubridate)
```

```{r class-instructor-variables}
pdata <- jsonlite::fromJSON(params$pdata)
ctable <- jsonlite::fromJSON(params$cdata)
ipay <- sum(ctable$final_pay, na.rm = TRUE)
```

Dear `r params$iname`,

Please find the details below based on the classes you taught at TYC this month.
The calculation of your payout is based on the following parameters:

| Base 0 Clients          | Base 1+ Clients         | PP7 (\*)              | Cap                   |
|-------------------------|-------------------------|-----------------------|-----------------------|
| `r dollar(pdata$base0)` | `r dollar(pdata$base1)` | `r dollar(pdata$pp7)` | `r dollar(pdata$cap)` |

(\*) PP7 = Per person starting with 7th Student

The classes you taught are shown below: (if you taught a virtual class as well, the total represents the combined number of clients)

```{=tex}
\begingroup\setlength{\LTleft}{0pt minus 500pt}\setlength{\LTright}{0pt minus 500pt}\fontsize{5pt}{7pt}\selectfont\addtolength{\tabcolsep}{-3pt}
```
```{r tbl, results='asis'}
#| include: true
#| echo: false

#gt(ctable[2:11], rowname_col = "instructor") |>
gt(ctable[2:11]) |>
   fmt_currency(columns = final_pay) |>
   fmt_integer(columns = c(at.s, lc.s, at.v, total)) |>
   cols_label(date = "Date", time = "Time", short_service = "Service", stype = "Stype", at.s = "Studio", lc.s = "LateC", at.v = "Virtual", total = "Total", hourly_pay_rate = "Pay Rate", final_pay = "Pay") |>
as_latex()
```

```{=tex}
\endgroup
```
Total Pay = `r dollar(ipay)`

Created on `r format(Sys.time(), "%B %d, %Y %H:%M:%S")`
